\href{https://github.com/Bleedingmetal}{github.com/Bleedingmetal}
\end{center}

\section*{Education}
\textbf{Worcester Polytechnic Institute} \hfill August 2023 - May 2027\\
Bachelor's in Computer Science \hfill GPA: 3.8

\section*{Professional Experience}
\textbf{Cognida.ai, Hyderabad, TG, India} \hfill May 2024 - August 2024\\
\textit{Software Development Intern}
\begin{itemize}
    \item Developed a chatbot to provide managers direct access to internal documents like financial reports and legal documents.
    \item Built an ingestion pipeline using llama\_index for document transformation and context-based vector search.
    \item Created a vector database using Chroma and Azure OpenAI, reducing query time from 5 minutes to 6 seconds.
    \item Implemented a streaming query engine for uninterrupted access to large datasets.
\end{itemize}

\textbf{Talitrix, Remote} \hfill June 2022 - August 2022\\
\textit{Software Development Intern}
\begin{itemize}
    \item Developed backend software for an ex-inmate monitoring watch tracking vitals and location.
    \item Increased data processing speed and reliability by 67\% using parallel processing for sensor input.
\end{itemize}

\section*{Skills}
\textbf{Programming:} C, Java, Git, C++, SQL, Python, Django, SciPy, Matplotlib, LangChain, Neural Networks, ML, NLP (SpaCy), Llama Index, Linux, React.js, Node.js, R, Matlab.\\
\textbf{Concepts:} Machine Organization, OOP, Data Structures \\& Algorithms, Linear Algebra, Discrete Math, Statistics, Probability, Databases, Vector Databases, Operating Systems.\\
\textbf{Languages:} Hindi, Gujarati, Tamil, Telugu

\section*{Projects}
\textbf{Buoyancy Simulator} (IBDP Extended Essay) \hfill October 2022 - December 2022
\begin{itemize}
    \item Developed Python code with Matplotlib, NumPy, and Pandas to simulate buoyancy effects based on temperature, volume, and density.
\end{itemize}

\textbf{Formula 1 AI Chat-Bot, HackUMass} \hfill November 2024
\begin{itemize}
    \item Developed an AI-powered F1 chatbot using React, Next.js, Tailwind CSS, and ChromaDB for real-time race strategy insights.
    \item Built a RAG system with Node.js, Express, and OpenAI embeddings for context-aware retrieval of F1 radio messages.
\end{itemize}

\section*{Honors and Awards}
\begin{itemize}
    \item WPI Dean’s List Academic Excellence Award (Fall 2023, Spring 2024)
    \item WPI Presidential Scholarship
    \item Second Place and Youngest CEO - TiE Young Entrepreneurs Competition
\end{itemize}

\end{document}
